#If you don't already have the required libraries installed in your environment install them using the next line  
#install.packages(c("neuralnet", "caret", "tidyverse", "mlbench", "e1071"))

#Incase you are already ready, import these libraries so as to start cooking

```{r}
library(neuralnet)
library(caret)
library(tidyverse)
library(mlbench)
library(e1071)

```
#importing dataset and getting an initial view of it

```{r}
data("PimaIndiansDiabetes")
df <- PimaIndiansDiabetes
str(PimaIndiansDiabetes)
ggplot(df, aes(diabetes, fill = as.factor(diabetes))) + geom_bar()

```
#Making diabetes values as binary numbers - 0, 1 reflecting diabetic or not

```{r}
df$binary <- ifelse(df$diabetes == "neg", 0, 1)
str(df)

```
#preparing model for evaluation

```{r}
rows <- createDataPartition(df$binary, times =1, p = .7, list = F)
train <- df[rows,]
test <- df[-rows,]

```
#diabetes and binary are representation of the same thing so we drop diabetes

```{r}
train <- train[,-9]
test <- test[,-9]
str(train)
str(test)

```
#training our model to make predictions. Roughly slicing 30-70 for our test-train datasets 

```{r}

model <- train(as.factor(binary) ~ ., data = train, method = "ranger",
               trControl = trainControl(method = "repeatedcv", number = 5, repeats = 5))

model

```
#making a confusion matrix to determine accuracy of our predict() method

```{r}
pred_train <- predict(model, train)
pred_test <- predict(model, test)

#pred_train

confusionMatrix(pred_train, as.factor(train$binary))
confusionMatrix(pred_test, as.factor(test$binary))

```
